---
title: "P8105_HW1_cc4778"
author: "Chee Kay Cheong"
date: "2022-09-19"
output: github_document
---

```{r, include = FALSE}
library(tidyverse)
```

# Problem 1
```{r load penguin, echo = FALSE}
data("penguins", package = "palmerpenguins")
```

#### A short description of the `penguins` dataset

The `penguins` dataset consists of `r ncol(penguins)` variables and `r nrow(penguins)` observations.

The variables name and their corresponding types are listed as below:

1. `species` : Factor with 3 levels 
   * Adelie
   * Chinstrap
   * Gentoo
  
2. `island` : Factor with 3 levels
   * Biscoe
   * Dream
   * Torgersen
  
3. `bill_length_mm` : numeric values

4. `bill_depth_mm` : numeric values

5. `flipper_length_mm` : integers

```{r mean flipper length, echo = FALSE}
mean_flip = mean(penguins$flipper_length_mm, na.rm = TRUE)
```

    * The mean flipper length (in mm) of the sampled penguin population is `r round(mean_flip, digits = 2)`.

6. `body_mass_g` : integers

7. `sex` : Factor with 2 levels
    * Female
    * Male
  
8. `Year` : Integers


#### Scatterplot

This is a scatterplot of flipper length versus bill length by the three groups of species.

```{r scatterplot, warning =  FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
```
```{r save graph, echo = FALSE, warning = FALSE}
ggsave("Scatterplot.pdf", height = 6, width = 10)
```


# Problem 2



