---
title: "P8105_HW1_cc4778"
author: "Chee Kay Cheong"
date: "2022-09-19"
output: github_document
---

```{r, include = FALSE}
library(tidyverse) 
```

# Problem 1

This is a preview of the `penguins` dataset.

```{r load penguin, echo = FALSE}
data("penguins", package = "palmerpenguins")
head(penguins, 10)
```

#### A short description of the `penguins` dataset

The `penguins` dataset consists of `r ncol(penguins)` variables and `r nrow(penguins)` observations.

The variables name and their corresponding types are listed as below:

1. `species` : Factor vector with 3 levels 
   * Adelie
   * Chinstrap
   * Gentoo
  
2. `island` : Factor vector with 3 levels
   * Biscoe
   * Dream
   * Torgersen
  
3. `bill_length_mm` : Double, numeric vector

4. `bill_depth_mm` : Double, numeric vector

5. `flipper_length_mm` : Integers, numeric vector 

```{r mean flipper length, echo = FALSE}
mean_flip = mean(penguins$flipper_length_mm, na.rm = TRUE)
```
    * The mean flipper length (in mm) of the sampled penguin population is `r round(mean_flip, digits = 2)`.

6. `body_mass_g` : Integers, numeric vector

7. `sex` : Factor vector with 2 levels
    * Female
    * Male
  
8. `Year` : Integers, numeric vector


#### Scatterplot

This is a scatterplot of flipper length versus bill length by the three groups of species.

```{r scatterplot, warning =  FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
```

I am exporting an image of this scatterplot as a pdf file and save it in my Rproject folder.
```{r save graph, eval = FALSE, warning = FALSE}
ggsave("Scatterplot.pdf", height = 6, width = 10)
```


# Problem 2

#### Creating a data frame

```{r data frame}
df = tibble(
  time_min = rnorm(10),
  on_time = time_min > 0,
  zone = c("A", "B", "C", "D", "E", "A", "B", "C", "D", "E"),
  color = factor(c("Green","Red","Yellow","Yellow","Yellow","Red","Green","Red","Yellow","Green"))
)
```

#### Taking the mean of each variable

```{r variables mean, warning = FALSE}
mean_time = mean(pull(df, time_min))
mean_ontime = mean(pull(df, on_time))
mean_zone = mean(pull(df, zone))
mean_color = mean(pull(df, color))
```

* The mean of the variable `time_min` is `r round(mean_time, digits = 2)`.
* The mean of the variable `on_time` is `r mean(mean_ontime)`.
* The mean of the variable `zone` is `r mean(mean_zone)`.
* The mean of the variable `color` is `r mean(mean_color)`.

Therefore, we know that we can take the means of a numeric vector and a logical vector, but not of a factor vector or a character vector.


#### Converting variables from one type to another

```{r convert, warning = FALSE, results = 'hide'}
as.numeric(df$on_time)
as.numeric(df$zone)
as.numeric(df$color)
```

1. In R, for a logical vector, `TRUE` is considered as 1 and `FALSE` is considered as 0. Hence, we can take a mean value of a logical vector. When we convert a logical vector into a numeric vector, it will return as '1' or '0' as well. 

2. Because the variable `zone` are made up of alphabet characters, when we try to convert it to numeric, it will return `NA`.

3. The factor vector has been converted to [1,2,3] three different numeric vectors as originally the factor vector has three levels. The default ordering of the factor vector is alphabetical. Those with lower alphabetical order will be assigned as '1', and so on.




